---
title: "Wild Data"
format: html
editor: visual
execute: 
  warning: false
  message: false 
---

## Libraries

```{r}
library(tidyverse)
library(here)
library(janitor)
library(dplyr)
```

## Read in Data 

```{r}

mack_verts <- read_csv(here::here("data", "AS00601.csv")) %>% clean_names()


```

## Now do this 

-   Store the 5th value in column \"WEIGHT\" as `mc_wt_5`. Check by looking at your data frame to confirm.

-   Store the 8th - 20th value in the \"LENGTH1\" column as `mc_length_8_20`. Check by looking at your data frame to confirm.

-   Store everything in column SAMPLEDATE as a vector called `mc_dates`

\

```{r}
mc_wt_5 <- mack_verts$weight[5]
mc_length_8_20 <- mack_verts$length1[8:20]
mc_dates <- mack_verts$sampledate
```

-   Create a subset that only contains observations for Pacific Giant Salamanders (species *Dicamptodon tenebrosus*, stored in`species` as `DITE`). Store the subset as `mc_salamanders`. *Hint:* see `dplyr::filter()`!

```{r}
mc_salamanders <- mack_verts %>% dplyr::filter(species == "DITE")
```

-   Create a scatterplot of length1 (snout-vent length in millimeters) versus weight (grams) for all salamanders in the subset you created above, `mc_salamanders`. Update axis labels, title, subtitle, and add a caption with the data source. Customize point color and size, possibly opacity, and theme.


```{r}
scatter_length1_weight <- ggplot(data = mc_salamanders, aes(x = length1, y = weight)) +
  geom_point(aes(color = weight)) + 
  scale_color_gradient(low = "blue", high = "orange")
  labs(title = "salamander weight by snout length", x = "snout length", y = "weight") +
  theme_dark()
scatter_length1_weight
```


-   Export your scatterplot as `salamander_size.png` to your figs folder.\

```{r}
ggsave(here::here("figs", "salamander_size.png"), height = 6, width = 7)
```



Similar to above, make a subset called mc_trout that only contains observations for cutthroat trout (species “ONCL”)
Create a scatterplot of length1 by weight for all trout in the dataset
Customize so that the point color depends on reach
Customize your color scheme (e.g. scale_color_manual())
Facet your plot by creek reach (facet_wrap(~...))
Update graph axis labels and title
Export your graph as cutthroat_size.png to the figs folder

```{r}
mc_trout <- mack_verts %>% filter(species == "ONCL")

trout_length <- ggplot(data = mc_trout, aes(x = weight, y = length1)) +
  geom_jitter(aes(color = reach)) +
  scale_color_manual(values = c("orange", "blue", "green")) +
  facet_wrap(~ reach)
trout_length
```

